Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-21 doc/PRF2022/PRF_main.tex
finishing up discussion

To estimate $h(\kk)$, 
the $N_b = 60$ JP
vesicle in Figure \ref{fig:s2esummary}(e) 
has arclength $L_x \approx 50$ nm. 
Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
Since our simulations are two-dimensional, we restrict our attention
to transversely invariant fluctuations where $n = 0$.
Substituting these values gives 
\begin{equation}
\label{eq:fourier_spectrum_upper}
\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
\end{equation}
For any moderate transverse depth, say $L_y > 4$ nm, the leading Fourier
coefficient has a magnitude less than $1$ nm with the remaining
coefficients dropping off to zero precipitously.  The expected
amplitudes coming from thermal fluctuations are therefore negligible
compared to particle size.  The elastic moduli for the Type II and
Type III phases are greater by a factor of two and five, respectively,
than for Type I (Figure~\ref{fig:fsummary}(c)), making thermal
fluctuation even more negligible in these cases.

The fact that the fluctuation amplitudes are small is not a consequence
of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$ agrees
with the experimental literature where micron sized vesicles observably
fluctuate.  Rather, larger energies are required to fluctuate membranes
over smaller wavelengths and these energies exceed available thermal
energy when the wavelengths approach tens of nanometers as demonstrated
above.

The calculated viscosities---14 mPa s for Type I and 21 mPa s for Type
II JP phases---are physically reasonable.  In two-dimensional dilute
suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2 +
O(\phi^3)$, where $\phi \ll 1$ is the volume
fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
Brady1983TheEV}. In Figures \ref{fig:s2esummary}(e)--(h), the volume
fraction is $\phi \approx 0.5$, which would correspond to a effective
shear viscosity of $4$ mPa s according to Einstein's viscosity
correction. Note, however, that since $\phi = 0.5$ is outside of the
dilute limit, one expects viscosities ten or more times that of water
\cite{Konijn2014ExperimentalSO}.

Nevertheless, further simulations are required to differentiate between
purely suspension effects and particles' preferred alignments. For
example, the difference between the values 14 mPa s for Type I and 21
mPa s for Type II JPs can be explained by the fact that the
multilamellar phase is more tightly packed than the bilayer phase
(Figure \ref{fig:s2esummary}(e)--(h)).  Furthermore, it seems that the
viscosity, and the tendency toward shear thinning in the case of Type
III JPs where viscosity is effectively infinite for low strain rates
(Figure \ref{fig:rheologysummary}(c)), is related to particle
coordination.  To leading order, a single particle coordinates with: one
neighbor in the apposing bilayer for Type I, two neighbors at the tail
and head interfaces for Type II, and four neighbors (front, back, left,
and right) for Type III.

\section{Conclusion}
\label{sec:conclusion}

In this work, we employ the newly developed JP model using
BIEs~\cite{Fu20, Fu2022_JFM} and tune the boundary conditions with
energy normalization to study the collective dynamics of amphiphilic
(BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under
various flowing conditions (quiescent flow, linear shear flow, and
Taylor-Green flow). Three quantities are computed to characterize the
dynamics of the collective configurations of JPs: free energy $F$,
strain parameter $E$, and scalar order parameter $S_2$. 
%We quantify how
%the collective hydrodynamics of JPs is affected by an external flow.
Under a given flow, we use these three measures of deformations to
quantify the differences in the collective dynamics between the three
types of JPs. These results, summarized below, provide general insight
into the dynamic control of active particles in a viscous suspension.

>>>>

To estimate $h(\kk)$, the $N_b = 60$ JP vesicle in
Figure~\ref{fig:s2esummary}(e) has arclength $L_x \approx 50$~nm. Our
prior work~\cite{Fu20,Fu2022_JFM} gave $\kappa \approx 20$ $\kbt$. Since
our simulations are two-dimensional, we restrict our attention to
transversely invariant fluctuations where $n = 0$. Substituting these
values gives 
\begin{equation}
\label{eq:fourier_spectrum_upper}
\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
\end{equation}
For any moderate transverse depth, say $L_y > 4$~nm, the leading Fourier
coefficient has a magnitude less than $1$~nm with the remaining
coefficients dropping off to zero precipitously. The expected amplitudes
coming from thermal fluctuations are therefore negligible compared to
particle size. The elastic moduli for the Type II and Type III phases
are greater by a factor of two and five, respectively, than for Type I
(Figure~\ref{fig:fsummary}(c)), making thermal fluctuation even more
negligible in these cases.

The fact that the fluctuation amplitudes are small is not a consequence
of stiffness. Quite the opposite, the value $\kappa = 20$~$\kbt$ agrees
with the experimental literature where micron sized vesicles observably
fluctuate. Rather, larger energies are required to fluctuate membranes
over smaller wavelengths and these energies exceed available thermal
energy when the wavelengths approach tens of nanometers as demonstrated
above.

The calculated viscosities---14~mPa~s for Type I and 21~mPa~s for Type
II JP phases---are physically reasonable. In two-dimensional dilute
suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2
+ O(\phi^3)$, where $\phi \ll 1$ is the volume
fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
Brady1983TheEV}. In Figures~\ref{fig:s2esummary}(e)--(h), the volume
fraction is $\phi \approx 0.5$, which would correspond to a effective
shear viscosity of $4$~mPa~s according to Einstein's viscosity
correction. Note, however, that since $\phi = 0.5$ is outside of the
dilute limit, one expects viscosities ten or more times greater than the
viscosity of water~\cite{Konijn2014ExperimentalSO}.

Nevertheless, further simulations are required to differentiate between
purely suspension effects and particles' preferred alignments. For
example, the difference between the values 14~mPa~s for Type I and
21~mPa~s for Type II JPs can be explained by the fact that the
multilamellar phase is more tightly packed than the bilayer phase
(Figures \ref{fig:s2esummary}(e)--(h)). Furthermore, it seems that the
viscosity, and the tendency toward shear thinning in the case of Type
III JPs where viscosity is effectively infinite for low strain rates
(Figure \ref{fig:rheologysummary}(c)), is related to particle
coordination. To leading order, a single particle coordinates with: one
neighbor in the apposing bilayer for Type I, two neighbors at the tail
and head interfaces for Type II, and four neighbors (front, back, left,
and right) for Type III.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

In this work, we employ the newly developed JP model using
BIEs~\cite{Fu20, Fu2022_JFM} and tune the boundary conditions with
energy normalization to study the collective dynamics of amphiphilic (BC
I), biased hydrophobic (BC II), and bipolar (BC III) JPs under various
flowing conditions (quiescent flow, linear shear flow, and Taylor-Green
flow). Three quantities are computed to characterize the dynamics of the
collective configurations of JPs: free energy $F$, strain parameter $E$,
and scalar order parameter $S_2$. 
%We quantify how
%the collective hydrodynamics of JPs is affected by an external flow.
Under a given flow, we use these three measures of deformations to
quantify the differences in the collective dynamics between the three
types of JPs. These results, summarized below, provide general insight
into the dynamic control of active particles in a viscous suspension.
